---
title: "Pairwise Comparison Analysis"
author: "Koki Sasagawa"
output:
  pdf_document: default
  html_notebook: default
---

```{r}
library(BradleyTerry2)
library(qvcalc)
# Specify file directory 
direct = './output/'
```

# BradleyTerryModel 
```{r}
# Load water source comparison results as binomial frequencies 
comparison_full <- read.csv(paste(file=direct, 'win_table_US(full).csv', sep=''))
head(comparison_full)
```
The one-sided model formula specifies the model for **'player ability'**, in this case the **'Relative preferability'**.  
The id argument specifies that 'source' is the name to be used for the factor that identifies the player.  
The estimated coefficients are the maximum likelihood estimates of $\lambda_2$, $\lambda_3$, $\lambda_4$ with $\lambda_1$. 

```{r}
model <- BTm(outcome = cbind(win1, win2), player1 = source1, player2 = source2, formula = ~source, id = 'source', data=comparison_full)
model
```
Get the relative preferability score of each water source using the function **'BTabilities'** which extracts estimates and standard errors for the log-ability scores $\lambda_1$, ..., $\lambda_k$. 

**Quasi variance (qv)** estimates are statistical approach that is suitable for communicating the effects of a categorical explanatory variables within a statistical model. In standard statistical models the effects of a categorical explanatory variable are assessed by comparing one category (or level) that is set as a benchmark against which all other categories are compared. 

The benchmark or reference category here is **Bottled water**. 

Analysis reveals whether or not each category differs from the reference category. 
```{r}
RPS <- BTabilities(model)
RPS
```
```{r}
comparison_full.qv <-qvcalc(RPS)
df <- data.frame(comparison_full.qv['qvframe'])
df
```
```{r}
# Label values rounded to the 5th decimal point
values = round(df$qvframe.estimate, 4)
values
```

```{r}
# Generate point labels 
library('latex2exp')
# Convert from int to string
point_labels <- paste(values)

for (val in 1:length(point_labels)){
  text <- c(point_labels[val], '$\\pm$', round(2*df$qvframe.quasiSE[val], 2))
  text <- paste(text, collapse=" ")
  point_labels[val] <-TeX(text)
}
```

Plot RPS scores $\pm$ 2*Quasi Standard error. 
Comparison Intervals - emphasis that they are constructed for inference about differences 
Quasi-variance: Control relative error, not absolute error
visual aid to inference about coefficient differences 
```{r}
x_axis <- c("Bottled Water", " Car Filter", "Public Water Fountain", "Tap Water (Home)")

png('./images/RPS_full.png', width=800, height=500)
plot(comparison_full.qv, levelNames=x_axis, main="Relative Preference Scores (RPS) with Quasi Standard Errors (All Respondents)", ylab="Estimated Preference Score", las=0, cex=1.2)
text(df$qvframe.estimate, labels=point_labels, pos=4, cex=1.0)
dev.off()
```


